R for Clinical Study Reports and Submission

### 2021-11-30 slides/workshop-slides.Rmd
minor fixes

---
title: "R for Clinical Study Reports and Submission"
subtitle: "ASA Princeton-Trenton Chapter, 2021"
author: "Yilong Zhang, Nan Xiao"
date: "October 2021"
output:
  mkdocs::mk_ioslides_presentation:
    mk_logo: "invent"
    mk_col_title: "white"
    mk_col_section: "teal"
    mk_class: "public"
    widescreen: true
---

>>>>

---
title: "R for Clinical Study Reports and Submission"
subtitle: "ASA Princeton-Trenton Chapter"
author: "Yilong Zhang, Nan Xiao"
date: "December 2021"
output:
  mkdocs::mk_ioslides_presentation:
    mk_logo: "invent"
    mk_col_title: "white"
    mk_col_section: "teal"
    mk_class: "public"
    widescreen: true
---
